### 2025-08-05 final-presentation/final.tex
presentations

\documentclass[aspectratio=169, compress, 12pt]{beamer}

@@

\usepackage{Custom}                         %%%%%%%%%%%%%%%%%%    (EDIT NAMES)
\usepackage{Custom-2}                         %%%%%%%%%%%%%%%%%%    (EDIT COLOURS)
\usepackage{AuxiliaryFiles/AuxiliaryFiles}  %%%%%%%%%%%%%    (DO NOT EDIT)

\begin{document}
\TitlePage        
\SectionPage    
\SubsectionPage    %%%% PAGE AT THE BEGINNIN OF A SECTION - IF NOT NEEDED, COMMENT IT
\ProgressBar       %%%% PROGRESS BAR ON THE RIGHT MARGIN - IF NOT NEEDED, COMMENT IT
\PageNumbering     %%%% SLIDES NUMBERING - IF NOT NEEDED, COMMENT IT

@@

\section{Comparative Study}
\subsection*{Agda}
\begin{frame}{Agda}

@@

    \item \textbf{Dependently typed functional programming language and proof assistant}.
    \item No separate tactic layer---proofs are constructed explicitly and directly.
    \item Uses \textbf{bidirectional type checking}, minimal kernel, and integrates normalization.
    \item Emphasizes explicitness and formal clarity over automation.
    \item Best suited for foundational work and educational purposes.

@@

\subsection*{Rocq (Coq)}
\begin{frame}{Rocq (Coq)}
    \item \textbf{Tactic-based interactive theorem prover} famous for large formalizations (e.g., Four Color Theorem).
    \item Kernel is based on Calculus of Inductive Constructions (CIC), written in Coq and extracted to OCaml.
    \item Proofs often built with backward reasoning using tactics---automation is heavily supported.
    \item Strong type-checking with bidirectional algorithms and conversion checking.
    \item Widely used for complex, real-world formal verification tasks.
\subsection*{Lean}
\begin{frame}{Lean}
    \item Developed at Microsoft, supports both \textbf{tactic-based and term-based} proofs.
    \item Kernel based on the Calculus of Inductive Constructions, implemented in C++/C.
    \item Allows seamless switching between tactic and term styles---user-friendly and flexible.
    \item Smart elaborator with coercion, backtracking, and overloading.
    \item Popular in research and education, especially for combinatorial and mathematical formalizations.
\section{Formalization Of Some proofs}

>>>>

\documentclass[aspectratio=169, 12pt]{beamer}

@@

\usepackage{Custom}                         %%%%%%%%%%%%%%%%%%    (EDIT NAMES)
\usepackage{Custom-2}                         %%%%%%%%%%%%%%%%%%    (EDIT COLOURS)
\usepackage{AuxiliaryFiles/AuxiliaryFiles}  %%%%%%%%%%%%%    (DO NOT EDIT)
\usepackage{graphics}
\begin{document}
\TitlePage        
\SectionPage    
\SubsectionPage    %%%% PAGE AT THE BEGINNIN OF A SECTION - IF NOT NEEDED, COMMENT IT
\ProgressBar       %%%% PROGRESS BAR ON THE RIGHT MARGIN - IF NOT NEEDED, COMMENT IT
\PageNumbering     %%%% SLIDES NUMBERING - IF NOT NEEDED, COMMENT IT

@@

\subsection*{Kernel}
\begin{frame}{Kernel: The Trusted Core}

@@

    \item The \textbf{kernel} is the minimal and most critical part of a proof assistant.
    \item It enforces the logical rules of the underlying formal system (e.g., type theory).
    \item Responsible for \textbf{validating every proof step} to guarantee correctness.
    \item Ensures \textbf{soundness and trustworthiness}; the rest of the system depends on its integrity.
    \item Typically very small and rigorously tested or formally verified to avoid bugs.
    \item Example: Agda’s kernel is written in Haskell and integrates normalization to check definitional equality.

@@

\subsection*{Tactic Engine}

\begin{frame}{Tactic Engine: Proof Construction Assistant}
\begin{itemize}
    \item The \textbf{tactic engine} supports users in constructing proofs interactively.
    \item It breaks complex proof goals into simpler subgoals using \textbf{proof strategies} called tactics.
    \item Provides \textbf{automation} for common proof patterns, speeding up proof development.
    \item Enables both \textbf{forward} and \textbf{backward} reasoning approaches.
    \item Even fully automated tactics rely on the kernel for final verification.
    \item Varies among assistants (Agda has minimal/no tactics, Coq and Lean have powerful tactic systems).
\end{itemize}
\end{frame}
\subsection*{ Language}

\begin{frame}{Formal Proof Language: Expressing Proofs Precisely}
\begin{itemize}
    \item This language allows expressing \textbf{definitions, propositions, and proofs} rigorously.
    \item Typically a \textbf{dependently typed language} so logical properties can be encoded as types.
    \item Provides \textbf{syntax and semantics} suitable for formal reasoning and machine checking.
    \item Enables users to write \textbf{human-readable yet unambiguous} formal proofs.
    \item Integrates smoothly with tactics and type checker to maintain correctness.
    \item Example languages: Agda’s core language, Coq’s Gallina, Lean’s dependent type language.
\end{itemize}
\end{frame}
\subsection*{Libraries}
\begin{frame}{Libraries: Reusable Verified Foundations}
\begin{itemize}
    \item Extensive collections of \textbf{formalized mathematics and algorithms} supporting new developments.
    \item Include \textbf{basic theories} such as arithmetic, algebra, logic, and set theory.
    \item Enable users to \textbf{build on existing verified results} without re-proving foundations.
    \item Libraries evolve and grow, fostering \textbf{collaboration and community sharing}.
    \item Well-maintained libraries reduce duplication and improve proof assistant adoption.
    \item Examples include Coq’s Standard Library, Agda Standard Library, Lean’s mathlib.
\end{itemize}
\end{frame}
\subsection*{User Interface}
\begin{frame}{User Interface: Proof Development Environment}
\begin{itemize}
    \item Provides \textbf{interactive tools} like IDEs, editor plugins, or command line interfaces.
    \item Features include \textbf{syntax highlighting, error reporting, real-time proof state visualization,} and \textbf{auto-completion}.
    \item Enhances \textbf{usability and productivity} for proof authors.
    \item Supports \textbf{integration with tactics and proof language} for seamless workflow.
    \item Examples: CoqIDE, Proof General, Emacs-mode for Agda, VS Code extensions.
    \item A good interface lowers the learning curve and makes formalization more accessible.
\end{itemize}
\end{frame}
\section{Comparative Study}
\begin{frame}{Comparative Table: Agda, Rocq (Coq), and Lean}

\begin{table}
\centering
\scalebox{0.75}{
    \begin{tabular}{|p{2cm}|p{4cm}|p{4cm}|p{4cm}|}
    \hline
    \small \textbf{Component} &  \small \textbf{Agda} & \small \textbf{Rocq (Coq)} & \small \textbf{Lean} \\
    \toprule
    \small \textbf{Proof Style} & \footnotesize Explicit term-based, manual proof writing & \footnotesize Tactic-based, automated backward reasoning & \footnotesize Both tactic-based and term-style \\

    \small \textbf{Kernel} & Minimal, written in Haskell, tight integration with normalization & Based on Calculus of Inductive Constructions (CIC), written in Coq (extracted to OCaml) & CIC-based, written in C++/C \\
    \small \textbf{Type Checking} & Bidirectional, transparent, normalization by evaluation & Bidirectional, heavy conversion, strong automation & Bidirectional, smart elaboration (coercion, backtracking, overloading) \\

    \small \textbf{Automation} & Limited (no tactics, minimal automation) & Extensive tactic engine and proof search & Advanced, seamless tactic/term mixing, smart elaborator \\

    \small \textbf{Use Cases} & Foundations, education, dependently typed programming & Large/complex formalizations, industrial-scale proofs & Research, education, combinatorial/mathematical formalizations \\
    \bottomrule
    \end{tabular}
}
\end{table}
\end{frame}

\section{Formalization Of Some proofs}
\subsection*{}
